TITLE

### 2021-02-14 outputs/paper/paper.Rmd
tidy up files

library(tidyverse)
library(bookdown)    # for cross referencing figures and graphs; referencing
library(scales)      # for fixing date axes
library(lubridate)   # for manipulating timeseries data
library(kableExtra)  # for nicer tables

>>>>

library(tidyverse)
library(bookdown)    # for cross referencing figures and graphs; referencing
library(kableExtra)  # for nicer tables
